Recent Advances in Reliable Transport Protocols\footnote{ Parts of the text in this chapter have appeared in the following publications by the same author(s): \cite{login}, \cite{mptcp-cc}, \cite{raiciu2012hard}, ~\cite{nowlan12fitting} and~\cite{iyengar10minion}.}

### 2013-07-25 Compiled/chapter5/main.tex
Full compiled
common latex and bibtex styles for all chapters
added page numbers and initial support for copyright, urls are now clickable
fixes

\newcommand{\CLASSINPUTinnersidemargin}{0.7in}
\newcommand{\CLASSINPUToutersidemargin}{0.7in}

@@

@@

@@

\title{Recent advances in reliable transport protocols\footnote{
Parts of the text in this chapter have appeared in the following
 publications by the same author(s): \cite{login}, \cite{mptcp-cc},
 \cite{raiciu2012hard}, ~\cite{nowlan12fitting} 
and~\cite{iyengar10minion}.}
}

\author{}

@@

@@

\bibliographystyle{plain}
\bibliography{ebook,rfc}

>>>>

%\newcommand{\CLASSINPUTinnersidemargin}{0.7in}
%\newcommand{\CLASSINPUToutersidemargin}{0.7in}

@@

\input{../commonstyle}

\input{copyright}

@@

\title{Recent Advances in Reliable Transport Protocols\footnote{
Parts of the text in this chapter have appeared in the following
 publications by the same author(s): \cite{login}, \cite{mptcp-cc},
 \cite{raiciu2012hard}, ~\cite{nowlan12fitting} 
and~\cite{iyengar10minion}.}
}

\author{Costin Raiciu, Janardhan Iyengar, Olivier Bonaventure}

\date{}

@@

\pagestyle{empty}

@@

\thispagestyle{empty}

@@

%\bibliographystyle{plain}

\input{../commonbibstyle}
\bibliography{ebook,rfc}
